Personality and political beliefs across the lifespan

### 2019-11-19 scripts/manuscript.Rmd
filter, mutate, and select

```{r setup, include = FALSE}
library(papaja)
library(rio)
library(here)
library(tidyverse)

data <- import(here("data", "EPB.csv"), setclass = "tbl_df")
```

@@

```{r cleaning}

>>>>

```{r setup, include = FALSE}
library(papaja)
library(rio)
library(here)
library(tidyverse)
library(psych)

data <- import(here("data", "EPB.sav"), setclass = "tbl_df")
```

@@

```{r filter}
#Removing particpants from the sample

#filter out preview mode (not real participants) and those who did not complete the survey
data <- data %>% 
  filter(DistributionChannel != "preview" & Progress == 100)

#filter out those who did not pass the attention checks
data <- data %>% 
  filter(Q6_8 == 6 & Q5_14 == 3)

#filter out those who took the survey too quickly (the time cut offs were predetermined and based on which condition the participant was randomly assigned to)
data <- data %>% 
  pivot_longer(cols = Video_DO_V4:Video_DO_V1, 
               names_to = "Video_DO", 
               values_to = "Value",
               names_prefix = "Video_DO_",
               values_drop_na = TRUE) %>% 
  filter(Video_DO == 'V1' & Duration__in_seconds_ >316 | 
           Video_DO == 'V2' & Duration__in_seconds_ > 340 | 
           Video_DO == 'V3' & Duration__in_seconds_ > 398 |
           Video_DO == 'V4' & Duration__in_seconds_ > 666 | 
           Video_DO == 'V5' & Duration__in_seconds_ > 565 | 
           Video_DO == 'V6' & Duration__in_seconds_ > 538) %>% 
  filter(Duration__in_seconds_ < 5000) #this person spent too long taking the survey
```

```{r aggregrateSEC}

#Aggregating the social and economic conservationism scale (SECs)
items <- c("Q3_1", "Q3_2","Q3_3","Q3_4","Q3_5","Q3_6","Q3_7","Q3_8","Q3_9","Q3_10","Q3_11","Q3_12" )

#econonmic conservatism subscale 
scaleKey <- c(0, 1, 0, 0, -1, 1, 0, 0, 1, 1, 0, 0)
economic <- scoreItems(keys = scaleKey, items = data[items], 
  totals = FALSE, missing = FALSE, min = 0, max = 100)
data <- data %>% 
  mutate(SEC_economic_conservatism = economic$scores[,1])

#social conservatism subscale
scaleKey <- c(-1, 0, 1, 1, 0, 0, 1, 1, 0, 0, 1, 1)
social <- scoreItems(keys = scaleKey, items = data[items], 
  totals = FALSE, missing = FALSE, min = 0, max = 100)
data <- data %>% 
  mutate(SEC_social_conservatism = social$scores[,1])
```

```{r aggregateTIPI}

#Aggregating big 5 traits (TIPI)
items <- c("Q4_1", "Q4_2", "Q4_3", "Q4_4", "Q4_5", "Q4_6", "Q4_7", "Q4_8", "Q4_9", "Q4_10")

#Extraversion
scaleKey <- c(1, 0, 0, 0, 0, -1, 0, 0, 0, 0)
extraversion <- scoreItems(keys = scaleKey, items = data[items], 
  totals = FALSE, missing = FALSE, min = 1, max = 7)
data <- data %>% 
  mutate(Extraversion = extraversion$scores[,1])

#Agreeableness
scaleKey <- c(0, -1, 0, 0, 0, 0, 1, 0, 0, 0)
agree <- scoreItems(keys = scaleKey, items = data[items], 
  totals = FALSE, missing = FALSE, min = 1, max = 7)
data <- data %>% 
  mutate(Agreeableness = agree$scores[,1])

#Conscientiousness
scaleKey <- c(0, 0, 1, 0, 0, 0, 0, -1, 0, 0)
consc <- scoreItems(keys = scaleKey, items = data[items], 
  totals = FALSE, missing = FALSE, min = 1, max = 7)
data <- data %>% mutate(Conscientiousness = consc$scores[,1])

#Emotional stability
scaleKey <- c(0, 0, 0, -1, 0, 0, 0, 0, 1, 0)
emo <- scoreItems(keys = scaleKey, items = data[items], 
  totals = FALSE, missing = FALSE, min = 1, max = 7)
data <- data %>% 
  mutate(Emotional_stability = emo$scores[,1])

#Openness to experiences
scaleKey <- c(0, 0, 0, 0, 5, 0, 0, 0, 0, -1)
open <- scoreItems(keys = scaleKey, items = data[items], 
  totals = FALSE, missing = FALSE, min = 1, max = 7)
data <- data %>% 
  mutate(Openness_to_experiences = open$scores[,1])
```

```{r select}
#selecting the variables that we want to use
data <- data %>% 
  select(ResponseId, Q7, Q8, Q9, Q10, Q11,
         SEC_economic_conservatism, SEC_social_conservatism,
         Agreeableness, Conscientiousness, Openness_to_experiences, Extraversion, Emotional_stability) %>% 
  rename(Gender = Q7, 
         Age = Q8, 
         Ethnicity = Q9, 
         Political_orientation = Q10,
         Political_affiliation = Q11,
         id = ResponseId) %>% 
  janitor::clean_names() %>% 
  characterize()
```

### 2019-11-19 scripts/manuscript.tex
filter, mutate, and select

We used R (Version 3.6.1; R Core Team, 2019) and the R-packages
\emph{here} (Version 0.1; Müller, 2017), \emph{papaja} (Version
0.1.0.9842; Aust \& Barth, 2018), and \emph{rio} (Version 0.5.16; C.-h.
Chan, Chan, Leeper, \& Becker, 2018) for all our analyses.

@@

@@

@@

>>>>

We used R (Version 3.6.1; R Core Team, 2019) and the R-packages
\emph{dplyr} (Version 0.8.3; Wickham, François, Henry, \& Müller, 2019),
\emph{forcats} (Version 0.4.0; Wickham, 2019a), \emph{ggplot2} (Version
3.2.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017),
\emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{purrr}
(Version 0.3.3; Henry \& Wickham, 2019), \emph{readr} (Version 1.3.1;
Wickham, Hester, \& Francois, 2018), \emph{rio} (Version 0.5.16; C.-h.
Chan, Chan, Leeper, \& Becker, 2018), \emph{stringr} (Version 1.4.0;
Wickham, 2019b), \emph{tibble} (Version 2.1.3; Müller \& Wickham, 2019),
\emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), and
\emph{tidyverse} (Version 1.2.1; Wickham, 2017) for all our analyses.

@@

\hypertarget{ref-R-purrr}{}
Henry, L., \& Wickham, H. (2019). \emph{Purrr: Functional programming
tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}

@@

\hypertarget{ref-R-tibble}{}
Müller, K., \& Wickham, H. (2019). \emph{Tibble: Simple data frames}.
Retrieved from \url{https://CRAN.R-project.org/package=tibble}

@@

\hypertarget{ref-R-ggplot2}{}
Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}.
Springer-Verlag New York. Retrieved from
\url{https://ggplot2.tidyverse.org}

\hypertarget{ref-R-tidyverse}{}
Wickham, H. (2017). \emph{Tidyverse: Easily install and load the
'tidyverse'}. Retrieved from
\url{https://CRAN.R-project.org/package=tidyverse}

\hypertarget{ref-R-forcats}{}
Wickham, H. (2019a). \emph{Forcats: Tools for working with categorical
variables (factors)}. Retrieved from
\url{https://CRAN.R-project.org/package=forcats}

\hypertarget{ref-R-stringr}{}
Wickham, H. (2019b). \emph{Stringr: Simple, consistent wrappers for
common string operations}. Retrieved from
\url{https://CRAN.R-project.org/package=stringr}

\hypertarget{ref-R-tidyr}{}
Wickham, H., \& Henry, L. (2019). \emph{Tidyr: Tidy messy data}.
Retrieved from \url{https://CRAN.R-project.org/package=tidyr}

\hypertarget{ref-R-dplyr}{}
Wickham, H., François, R., Henry, L., \& Müller, K. (2019). \emph{Dplyr:
A grammar of data manipulation}. Retrieved from
\url{https://CRAN.R-project.org/package=dplyr}

\hypertarget{ref-R-readr}{}
Wickham, H., Hester, J., \& Francois, R. (2018). \emph{Readr: Read
rectangular text data}. Retrieved from
\url{https://CRAN.R-project.org/package=readr}
